Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Change section title; we're not indistinguishable yet.
Performance measurements for future work.
Put active scanning earlier in background.

% I'm thinking of recasting this as three challenges:
%  1. Content blocking.
%  2. Endpoint blocking.
%  3. Active scanning.
% We have something to say for all three and related work falls into one or
% more of those categories.
%
% "Cover your ACKs" talks about "unobservability" and "unblockability," maybe
% isomorphic to our "blocking by content" and "blocking by endpoint."

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by endpoint.
Blocking by content means that the censor inspect packet or flow payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
Blocking by endpoint means that the censor forbids all communication with certain
network addresses, whatever the content of the communication.
The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
by making it difficult to scan for proxies;
by having sufficiently many proxies;
or by colocating proxies with high-value services, to block which would incur collateral damage.
Effective proxy-based circumvention requires that both these challenges be addressed.

@@

Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.
They confirmed an earlier discovery of Wilde~\cite{wilde} that the firewall identifies Tor relays using more than passive monitoring:
it actively probes destination addresses to see if they speak the Tor protocol, and if so,
blocks them for the future.
(At the time, the firewall identified potential Tor connections for future probing by looking for a distinctive
list of TLS ciphersuites---a failure of obfuscation.) %\cite{bug4744}
The discovery of Chinese active probing was the motivation for probing resistance in ScrambleSuit
and in our work.

@@

\section{Making traffic characteristics indistinguishable}
\label{sec:trafficstatistics}

@@

>>>>

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by endpoint.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
Blocking by endpoint is based on \emph{whom you are speaking to},
and blocking by content is based on \emph{what you are saying}.
A skilled censor will do both, and effective circumvention requires meeting both challenges.
An endpoint-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.

To the above challenges we may add the related challenge of active scanning for proxies.
Though a circumvention protocol may be difficult to identify on the wire,
it may nevertheless be easy to scan for servers that speak the protocol,
and thereafter block the server by its address.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by actively scanning destination addresses to see if they speak the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and in this work.

@@

@@

\section{Camouflage of traffic characteristics}
\label{sec:trafficstatistics}

@@

% Performance measurements
